---
title: "STA513 HW2"
author: "John Behr"
date: " "
output:
  html_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_caption: yes
    number_sections: yes
    theme: readable
  pdf_document: 
    toc: yes
    toc_depth: 4
    fig_caption: yes
    number_sections: yes
    fig_width: 5
    fig_height: 4
  word_document: 
    toc: yes
    toc_depth: 4
    fig_caption: yes
    keep_md: yes
---
<style type="text/css">

div#TOC li {
    list-style:none;
    background-image:none;
    background-repeat:none;
    background-position:0;
}
h1.title {
  font-size: 20px;
  color: DarkRed;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkRed;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
  text-align: center;
}
h1 { /* Header 3 - and the author and data headers use this too  */
    font-size: 22px;
    font-family: "Times New Roman", Times, serif;
    color: darkred;
    text-align: center;
}
h2 { /* Header 3 - and the author and data headers use this too  */
    font-size: 18px;
    font-family: "Times New Roman", Times, serif;
    color: navy;
    text-align: left;
}

h3 { /* Header 3 - and the author and data headers use this too  */
    font-size: 15px;
    font-family: "Times New Roman", Times, serif;
    color: navy;
    text-align: left;
}

h4 { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
    font-family: "Times New Roman", Times, serif;
    color: darkred;
    text-align: left;
}
</style>

```{r setup1, include=FALSE}
# code chunk specifies whether the R code, warnings, and output 
# will be included in the output files.
if (!require("tidyverse")) {
   install.packages("tidyverse")
   library(tidyverse)
}
if (!require("knitr")) {
   install.packages("knitr")
   library(knitr)
}
# knitr::opts_knit$set(root.dir = "C:/Users/75CPENG/OneDrive - West Chester University of PA/Documents")
# knitr::opts_knit$set(root.dir = "C:\\STA490\\w05")

knitr::opts_chunk$set(echo = TRUE,       
                      warning = FALSE,   
                      result = TRUE,   
                      message = FALSE)
```



## Iris Dataset Plot Manipulation

```{r setup2, include=TRUE}
library(ggplot2)
ggplot(data = iris, mapping = aes(x = Sepal.Length, y = Sepal.Width)) +
geom_point(pch = 5)+    
labs(x = "Sepal Length",y = "Sepal Width",title = "Sepal Length VS. Width" )+
theme(plot.title = element_text(face = "bold", size = 10,
                                             family = "sans", 
                                             color = "darkred",
                                             hjust = 0.5), 
axis.title.x = element_text(color = "Gold",
face = "italic",
family = "serif",hjust = 0.5),
axis.title.y = element_text(color = "Black",face = "bold",vjust = 0.5),
axis.ticks = element_line(color = "Black", 
                                             size = 0.5),
axis.line = element_line(color = "Black", size = 1, linetype = "solid"),
                   
axis.text.x = element_text(face="plain", color="Black", size=11, angle=360),
axis.text.y = element_text(face="plain", color="Black", size=11, angle=45),
legend.background = element_rect(fill = "white", size = 0.1, color = "darkgreen"),
legend.justification = c(0.9, 0.8),legend.position = "bottom",
panel.grid.major = element_line(color = "Gold",size = 0.1),
panel.grid.minor = element_blank())
```


## Penguin Dataset Manipulation

```{r setup3, include=TRUE}
library(readr)  # for read_csv
library(knitr)  # for kable
myfile <- "https://raw.github.com/johnbehr23/sta553/master/w02-penguins.csv"
Penguins <- read_csv(myfile)


Penguins.1 <- Penguins[complete.cases(Penguins), ]
print(Penguins.1)


new.Penguins.id02 = which(Penguins.1$island == "Biscoe" | Penguins.1$island == "Torgersen")
Penguins.1 = Penguins.1[new.Penguins.id02,]
Penguins.1
print(Penguins.1)


Penguins.1 <- subset(Penguins.1, body_mass_g > 3500 & body_mass_g < 5000,
select=c(species,island,bill_length_mm,bill_depth_mm,flipper_length_mm,body_mass_g,sex,year))


Penguins.1$BMI <- (Penguins.1$body_mass_g / 4000)


Penguins.1 = select(Penguins.1,species,island,bill_length_mm,bill_depth_mm,flipper_length_mm,BMI)
str(Penguins.1)
```

## Penguin Plot


```{r setup4, include=TRUE}
library(ggplot2)
ggplot(data = Penguins.1, mapping = aes(x = bill_length_mm, y = bill_depth_mm)) +
    geom_point(pch = 5)+    
        labs(    x = "Bill Length",
                 y = "Bill Depth",
                 title = "Bill Length VS. Bill Depth" )+
  
              theme(plot.title = element_text(face = "bold", 
                                             size = 10,
                                             family = "sans", 
                                             color = "darkred",
                                             hjust = 0.5), # left(0),right(1)
                   # Labels of axes 
                   axis.title.x = element_text(color = "Gold",
                                               face = "italic",
                                               family = "serif",
                                               hjust = 0.5),
                   axis.title.y = element_text(color = "Purple",
                                               face = "bold",
                                               vjust = 0.5),
                   axis.ticks = element_line(color = "Black", 
                                             size = 0.5),
                   axis.line = element_line(color = "Black", 
                                            size = 1, 
                                            linetype = "solid"),
                   # Axis tick marks
                   axis.text.x = element_text(face="plain", 
                                              color="purple", 
                                              size=11, 
                                              angle=360),
                   axis.text.y = element_text(face="plain", 
                                              color="Purple", 
                                              size=11, 
                                              angle=45),
                   # Features of legend
                   legend.background = element_rect(fill = "white", 
                                                    size = 0.1, 
                                                    color = "darkgreen"),
                   legend.justification = c(0.9, 0.8),
                   legend.position = "bottom",
                   ## Panel grid
                   panel.grid.major = element_line(color = "Gold", 
                                                   size = 0.1),
                   panel.grid.minor = element_blank())
  
```

## Paragraph About the Relationship 

As you can see from the graph in the section above there is a clear relationship between Bill length and Bill Depth. It is clear to see that when there is a higher Bill length there is a lower Bill depth, and vise versa, when there is a higher Bill Depth there is a lower Bill length. This shows that there is an inverse relationship between the two variables.

